
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{resume}

\usepackage[left=0.4 in,top=0.3 in,right=0.4 in,bottom=0.3in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Muhammad Arya Hanif}
\address{Yogyakarta, Indonesia}
\address{+6285173342248 \\ aryasenaria@gmail.com}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Nuclear Engineering} \hfill {Jul 2025}
\\
Universitas Gadjah Mada
\\
Yogyakarta, Indonesia

{\bf iOS Developer} \hfill {Dec 2025}
\\
Apple Developer Academy @Binus Bali
\\
Bali, Indonesia

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills and Interests}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming & Python, Swift, SwiftUI, Git, \\& Shell Script\\
DataScience & PyTorch, OpenCV, NumPy, Pandas, Scikit-Learn, \\& SciPy\\
Ops & Linux, Docker, Railway, Flask, \\& npm, ngrok\\

\end{tabular}

\end{rSection}

%-------------------------------------------------------------------------------
%	PROJECTS
%-------------------------------------------------------------------------------

\begin{rSection}{Projects}

\begin{rSubsection}{Sealens}{Jul 2025 - Present}{AI Engineer}{}

\item Held an in depth research regarding possible solution concept that could help coral restoration communities.
\item Conduct technical feasibilities and CI for iOS development.
\item Designed and implemented a comprehensive end-to-end ML pipeline covering dataset creation, video preprocessing, object detection, deep feature extraction, clustering, classification, re-identification, quantitative evaluation, and deployment-ready inference flows.
\item Built a modular and scalable MLOps framework leveraging DVC to version-control 60k+ images, raw videos, cleaned datasets, model checkpoints, embeddings, and experiment artifacts, ensuring full reproducibility across the machine learning lifecycle.
\item Developed and benchmarked multiple object detection and classification models—including YOLOv11/v12, ResNet, Vision Transformers, Siamese networks, and custom CNN architectures—to support experimentation and continuous model improvement.
\item Created an automated cluster analysis system using DBSCAN, KMeans, and PCA to cluster the cropped images.

\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Monte Carlo Particle Transportation Simulation}{Jun 2023 - Jul 2024}{Project Owner}{}
\item Developed radiation dose distribution heatmap visualizations to correct misunderstandings in radiotherapy shielding design.
\item Compared radiation dose between simulation, analytic calculation and real measurement of bunker in Hasan Sadikin Public Hospital.

\end{rSubsection}

\end{rSection}

%--------------------------------------------------------------------------------------
%   EXPERIENCE
%--------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Dr. Hasan Sadikin Public Hospital}{Dec 2022 - Feb 2023}{Medical Physics Intern}{}

\item Executed supervised patient-specific treatment planning on linear accelerator and teletherapy.
\item Performed patient specific treatment planning and Quality Assurance \& Quality Control for radiodiagnostic, radiotherapy and nuclear medicine departments.

\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Electronics and Instrumentation Lab}{Jan 2021 - Jun 2021}{Teaching \& Lab Assistant}{}
\item Initiated curriculum update for lab learning modules and pre-/post-test assessments for post covid classes.
\item Monitored assessments and grading procedures for 100+ students across department.
\item Assisted students with instrumentation tools, sensors, measurement devices, and troubleshooting during practical sessions.

\end{rSubsection}

\end{rSection}

%--------------------------------------------------------------------------------------
%   SUMMARY
%--------------------------------------------------------------------------------------

\begin{rSection}{Summary}

Motivated, detail-oriented engineer with a strong passion for learning, experimenting, and solving complex problems. I enjoy building practical solutions from scratch, exploring new technologies, and improving systems with structured, data-driven thinking. Experienced on using python for particle simulations for nuclear health application and ML pipeline for video based fish identification application. I have been daily driving unix based operating system for four years. I am proficient with advanced Git workflows including interactive rebasing, custom patch creation and clean version control.

\end{rSection}

\end{document}
